Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-29 analysis/paper/paper.Rmd
Move statement about journals' role to workflow section
Capitalise "Contributions" to match other headings' format
Correct text on analysis findings

There was no effect of article class found.

Articles with a molecular focus tended to be more likely ranked high for reproducibility and openness but the difference was not strong enough to be detected with the analysis used.

Articles published in journals with a larger five year impact factor were more likely to be more open and reproducible but the analysis was unable to detect any differences.

@@

@@

# Authors' contributions

>>>>

There was no effect of article class or impact factor found.

Articles with a molecular focus skewed to a higher ranking reproducibility and openness but the difference was not strong enough to be detected with the analysis used.

@@

Journals can encourage authors to deposit their data and code by providing instruction for how to deposit the data and code in a repository and mint a DOI to accompany these resources.

@@

# Authors' Contributions
